Mining the human microbiome for clinical insight

### 2018-12-20 24hr/24hr_ms.tex
Working version of 24hr chapter and supplement

\begin{figure}[h]
\begin{center}
    \includegraphics{fig1_catchment_selection.png}
    \caption{Definition and identification of residential catchments. (A). Integrating data from sewage network and flow, manhole locations, land usage, and demographic data allows for the selction of carefully curated residential manholes. (B) Upstream residential catchment vs. downstream catchment.}\label{24hr:fig1}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
    \includegraphics{fig2_upstream_downstream.png}
    \caption{Upstream samples find more human-derived metabolites and bacteria. (A) Abundance of metabolite features in upstream vs. downstream sample (left) and volcano plot showing fold change vs. p-value (right). (B) Residential sewage sample (``Sewer'') contains more human-associated bacteria than downstream sample (``WWTP''). (C) Abundance of various confirmed human-associated metabolites in upstream vs. downstream sample.}\label{24hr:fig2}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
    \includegraphics{fig3_diurnal_dynamics.png}
    \caption{Human and environmental compartments reflect human diurnal dynamics. (A) Sampling campaign and schematic of expected human activity. (B) \textit{Top}: average flow rate in residential manhole. \textit{Bottom}: total ion count of M1 and M2 metabolite clusters. (C) Number of human-associated metabolites confirmed in M1 vs. M2 clusters. (D) \textit{Top}: average flow rate in residential manhole. \textit{Top middle}: Relative abundance of two OTU clusters, O1 and O2. \textit{Bottom middle}: Phylum-level taxonomic composition of bacterial cluster O1. \textit{Bottom}: Phylum-level taxonomic composition of bacterial cluster O2.}\label{24hr:fig3}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
    \includegraphics{fig4_urine_fecal_markers.png}
    \caption{Confirmed urinary and fecal biomarkers reflect human activity and behavior. (Top left) Average flow rate in residential manhole. (Bottom left) Total ion count of alpha-phenylacetylglutamine (PAG), a confirmed human urinary marker. (Top right) Total ion count of confirmed bile acids, human fecal markers. (Bottom right) Total ion count of urobilinogen, a confirmed human fecal marker. }\label{24hr:fig4}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
    \includegraphics{fig5_mining_big_data.png}
    \caption{Mining untargeted data suggests identification of human health, behavioral, and lifestyle biomarkers. Heatmap of metabolite feature abundance over 24-hour samplings, with putatively identified metabolites labeled. Metabolites labeled with opaque circles were confirmed with analytical standards or MS2 matching. Labels with transparent circles were identified via mass-matching neutral mass with HMDB metabolites.}\label{24hr:fig5}
\end{center}
\end{figure}

>>>>

\begin{figure}[h]
\begin{center}
    \includegraphics[width=\textwidth]{{24hr/figures/fig1_catchment_selection.png}}
    \caption{Definition and identification of residential catchments. (A). Integrating data from sewage network and flow, manhole locations, land usage, and demographic data allows for the selction of carefully curated residential manholes. (B) Upstream residential catchment vs. downstream catchment.}\label{24hr:fig1}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
    \includegraphics[width=\textwidth]{{24hr/figures/fig2_upstream_downstream.png}}
    \caption{Upstream samples find more human-derived metabolites and bacteria. (A) Abundance of metabolite features in upstream vs. downstream sample (left) and volcano plot showing fold change vs. p-value (right). (B) Residential sewage sample (``Sewer'') contains more human-associated bacteria than downstream sample (``WWTP''). (C) Abundance of various confirmed human-associated metabolites in upstream vs. downstream sample.}\label{24hr:fig2}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
    \includegraphics[width=\textwidth]{{24hr/figures/fig3_diurnal_dynamics.png}}
    \caption{Human and environmental compartments reflect human diurnal dynamics. (A) Sampling campaign and schematic of expected human activity. (B) \textit{Top}: average flow rate in residential manhole. \textit{Bottom}: total ion count of M1 and M2 metabolite clusters. (C) Number of human-associated metabolites confirmed in M1 vs. M2 clusters. (D) \textit{From top}: Average flow rate in residential manhole; relative abundance of two OTU clusters, O1 and O2; phylum-level taxonomic composition of bacterial cluster O1; phylum-level taxonomic composition of bacterial cluster O2.}\label{24hr:fig3}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
    \includegraphics[width=\textwidth]{{24hr/figures/fig4_urine_fecal_markers.png}}
    \caption{Confirmed urinary and fecal biomarkers reflect human activity and behavior. (Top left) Average flow rate in residential manhole. (Bottom left) Total ion count of alpha-phenylacetylglutamine (PAG), a confirmed human urinary marker. (Top right) Total ion count of confirmed bile acids, human fecal markers. (Bottom right) Total ion count of urobilinogen, a confirmed human fecal marker. }\label{24hr:fig4}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
    \includegraphics[width=\textwidth]{{24hr/figures/fig5_mining_big_data.png}}
    \caption{Mining untargeted data suggests identification of human health, behavioral, and lifestyle biomarkers. Heatmap of metabolite feature abundance over 24-hour samplings, with putatively identified metabolites labeled. Metabolites labeled with opaque circles were confirmed with analytical standards or MS2 matching. Labels with transparent circles were identified via mass-matching neutral mass with HMDB metabolites.}\label{24hr:fig5}
\end{center}
\end{figure}

### 2018-12-20 chap_aspiration.tex
Add percnorm and 24hr to intro, label all chapters
Working version of 24hr chapter and supplement

\chapter{Multi-site sampling reveals altered relationships in aerodigestive microbiomes of children with swallowing dysfunction}

@@

\bigskip
\bigskip
\noindent
The tables and figures are at the end of the Chapter. The Supplementary Information is in Appendix A.

>>>>

\chapter{Multi-site sampling reveals altered relationships in aerodigestive microbiomes of children with swallowing dysfunction}\label{chap:aspiration}

@@

\bigskip
\bigskip
\noindent
The tables and figures are at the end of the Chapter. The Supplementary Information is in Appendix \ref{app:aspiration}.

### 2018-12-20 chap_meta-analysis.tex
Add percnorm and 24hr to intro, label all chapters
Working version of 24hr chapter and supplement

\chapter{Meta-analysis of gut microbiome studies identifies disease-specific and shared responses}

@@

\bigskip
\bigskip
\noindent
The figures are at the end of the chapter. The Supplementary Information is in Appendix B.

>>>>

\chapter{Meta-analysis of gut microbiome studies identifies disease-specific and shared responses}\label{chap:meta-analysis}

@@

\bigskip
\bigskip
\noindent
The figures are at the end of the chapter. The Supplementary Information is in Appendix \ref{app:meta-analysis}.
